<!---
rmarkdown::render('01-intro.Rmd', "html_document", paste("_posts/", Sys.Date(), "-Flood-report-2.html", sep = ""), runtime="shiny")

or to make shiny work:
---
output:
  html_document
runtime:
  shiny
---

or 
---
title: "test"
author: FKB
date: "`r Sys.Date()`"
output:
  html_document
---


This is a markdown and rmarkdown comment
 md_document:
    variant: markdown_github
always_allow_html: yes
-->



# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r echo=FALSE, message=FALSE, eval=FALSE}
source('global.R')
# source('plotting_functions.R')
# flomtabell
# model4 <- HBV_past_year

model_1 <- HBV_2014
model_2 <- HBV_2016
model_3 <- DDD
selected_nbname <- "2.11-narsjo"

variable_1 <- c("SimRaw", "SimCorr", "SimL50", "SimH50")
variable_2 <- c("SimRaw", "SimCorr", "SimP50")
variable_3 <- c("DDD.Sim", "Obs")  
      
subset2plot_m1 <- dplyr::filter(model_1, nbname %in% selected_nbname & Type == "Runoff" & Variable %in% variable_1) 
subset2plot_m2 <- dplyr::filter(model_2, nbname %in% selected_nbname & Type == "Runoff" & Variable %in% variable_2) 
subset2plot_m3 <- dplyr::filter(model_3, nbname %in% selected_nbname & Type == "Runoff" & Variable %in% variable_3) 
# subset2plot_m1 <- dplyr::filter(model_1, nbname %in% station & Type == "Runoff" & Variable %in% variable_1)             
#                choices = unique(filter(model_4, Type == "Runoff")$Variable), multiple = TRUE) 
# c("Obs", "Sim"), multiple = TRUE) 
# subset2plot_rl <- dplyr::filter(return_levels, nbname %in% station & Type %in% type_rl) 
      
multimod_forecast_plot(subset2plot_m1, subset2plot_m2, subset2plot_m3)

```

Blabla
*Blabla*
**Blabla**

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

Ok, let's see if this whole thing works!
try again

test of embedding a piece of shiny app

```{r echo=FALSE, message=FALSE}
source('global.R')

shinyApp(
  
  ui = fluidPage(
                          mapModuleUI("multistation_map", multiple = TRUE),
                          multimod_forecast_selection_modUI("multistation_plot"),
                          forecast_plot_modUI("multistation_plot")
  ),
  
  server = function(input, output) {
     input4multi_forecast_plot <- callModule(mapModule,"multistation_map")
  callModule(multimod_forecast_plot_mod,"multistation_plot", input4multi_forecast_plot, HBV_2014, HBV_2016, DDD, HBV_past_year, flomtabell)
  
  },
  
  options = list(height = 500)
)
```

