

<!---
Either render the file this way:
rmarkdown::render('daily_report.Rmd', "html_document", 
paste("_posts/", Sys.Date(), "-Flood-report.html", sep= ""))

or copy those specificxations above:

---
title: "test"
author: "FKB"
date: '`r Sys.Date()`'
output: html_document
---


---
output: word_document
always_allow_html: yes
---
-->



# Literature

Let's try to integrate the first tab of the shiny app.


```{r echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
source('global.R')
# source('plotting_functions.R')
# source('plot_modules.R')
# source('mapping_functions.R')
# source('map_modules.R')

x <- 2+2

single_station_map(stations, selected_nbname = "2.11-narsjo")

```


How this did work?

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
source('global.R')
# source('plotting_functions.R')
# flomtabell
# model4 <- HBV_past_year

model_1 <- HBV_2014
model_2 <- HBV_2016
model_3 <- DDD
selected_nbname <- "2.11-narsjo"

variable_1 <- c("SimRaw", "SimCorr", "SimL50", "SimH50")
variable_2 <- c("SimRaw", "SimCorr", "SimP50")
variable_3 <- c("DDD.Sim", "Obs")  
      
subset2plot_m1 <- dplyr::filter(model_1, nbname %in% selected_nbname & Type == "Runoff" & Variable %in% variable_1) 
subset2plot_m2 <- dplyr::filter(model_2, nbname %in% selected_nbname & Type == "Runoff" & Variable %in% variable_2) 
subset2plot_m3 <- dplyr::filter(model_3, nbname %in% selected_nbname & Type == "Runoff" & Variable %in% variable_3) 
# subset2plot_m1 <- dplyr::filter(model_1, nbname %in% station & Type == "Runoff" & Variable %in% variable_1)             
#                choices = unique(filter(model_4, Type == "Runoff")$Variable), multiple = TRUE) 
# c("Obs", "Sim"), multiple = TRUE) 
# subset2plot_rl <- dplyr::filter(return_levels, nbname %in% station & Type %in% type_rl) 
      
multimod_forecast_plot(subset2plot_m1, subset2plot_m2, subset2plot_m3)

```

Blabla


```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
